Ceph Parallel File System Evaluation Report

### 2013-08-30 conclusion.tex
changes here and there

Ceph is built on the assumption that the underlying hardware components
are unreliable, with little or no redundancy and failure detection capability.
This assumption is not valid for high-end HPC centers like ours. We have
disabled replication for pools, we haven't measured and quantified
processing overhead and we do not know yet if this would be significant.

Ceph performs \textbf{metadata + data} journaling, which is fine for host
systems that have locally attached disks. However, this presents a problem in
DDN SFA10K-like hardware, where the backend LUNs are exposed as block devices
through IB over SRP protocol. The journaling write requires twice the
bandwidth compared to Lustre-like meta data-only journaling mechanism. For
Ceph to be viable in large-scale capability HPC environments like ours,
journaling operations will need further design and more engineering efforts.

In our earlier tests, we experienced large performance swings during different
runs, low read performance when transfer size is small, and I/O errors tend to
happen when system is under stress (more clients and large transfer sizes).
However, with systematic performance engineering and development efforts, we
have seen a steady improvement through different releases. As of now, Ceph
system on our testbed is able to perform close to 80\% of raw hardware
capability at RADOS level and close to 70\% at file system level. This is
still no comparison to Lustre yet, but by no means a small feat for such a
\textit{young} technology. It is, in fact, a very respectable level of
performance.

>>>>

Ceph is built on the assumption that the underlying hardware components are
unreliable, with little or no redundancy and failure detection capability.
This assumption is not valid for high-end HPC centers like OLCF. We have
disabled replication for pools, haven't measured and quantified processing
overhead, and we do not know yet if this would be significant. Investigating
this remains as a future work.

Ceph performs \textbf{metadata + data} journaling, which is fine for host
systems that have locally attached disks. However, this presents a problem in
DDN SFA10K-like hardware, where the backend LUNs are exposed as block devices
through IB over SRP protocol. The journaling write requires twice the
bandwidth compared to Lustre-like meta data-only journaling mechanism. For
Ceph to be viable in large-scale capability HPC environments like OLCF,
journaling operations need further design and more engineering efforts.

In our earlier tests, we experienced large performance swings during different
runs, low read performance when transfer size is small, and I/O errors tend to
happen when system is under stress (more clients and large transfer sizes).
However, with systematic performance engineering and development efforts, we
have seen a steady improvement through different releases. As of now, Ceph
system on our testbed is able to perform close to 80\% of raw hardware
capability at RADOS level and close to 70\% at file system level (after
accounting for journaling overheads) . This is still no comparison to Lustre
yet, but by no means a small feat for such a \textit{young} technology. It is,
in fact, a very respectable level of performance.

### 2013-08-30 introduction.tex
changes here and there

Oak Ridge Leadership Computing Facility (OLCF)\footnote{This research was
supported by, and used the resources of, the Oak Ridge Leadership Computing
Facility, located in the National Center for Computational Sciences at ORNL,
which is managed by UT Battelle, LLC for the U.S. DOE (under the contract No.
DE-AC05-00OR22725).} at Oak Ridge National Laboratory (ORNL) has a long history
of deploying and running very-large-scale high-performance computing (HPC)
systems\footnote{\url{http://www.top500.org/site/48553}}. The facility hosted
the Jaguar supercomputer up until recently, which was upgraded to the Titan
supercomputer. In order to satisfy the I/O demand of such supercomputers (as
well as, other OLCF computational, analysis, and visualization clusters), OLCF
also hosts large-scale file and storage systems. Lustre has been OLCF's choice
as the distributed parallel file system.  The latest incarnation of such
large-scale file systems hosted at OLCF is Spider II\cite{spider2}. Spider II
is the forklift-upgrade of its predecessor, Spider, which was deployed in 2008.
Spider II, deployed in 20013, is designed to operate at over 1 TB/s peak
aggregate I/O throughput and has a 40 PB of raw disk capacity. As the scratch
file system connected to a leadership computing platform at the scale of Titan,
Spider II emphasizes \textit{capability} over \textit{capacity}. However, we
also recognize that there are a wide variety of scientific data and workloads
with different performance and data access requirements (e.g., RESTful
interface, S3-like API, cloud solution integration) which might not be
efficiently serviced by Lustre. OLCF is constantly evaluating new and emerging
file and storage system technologies.

@@

In comparison to other parallel file
systems, Ceph has a number of distinctive features:

\begin{comment}
\begin{itemize}

@@

As interesting and feature-rich as Ceph may be,  scalability and performance
are our top priorities due to the unique requirements our environment.  As part
of this study, we set up a dedicated testbed within OLCF to understand and
evaluate Ceph.  Our goal was to investigate the feasibility of using the Ceph
for our future HPC storage deployments. This paper presents our experience,
results, and observations.  While evaluating our results, please keep in mind
that Ceph is still a relatively \textit{young} parallel file system and its
code base is changing rapidly. In between releases, we often experienced
different stability and performance outcomes.  We will try to make clear in the
writing when such changes occurred.

>>>>

Oak Ridge Leadership Computing Facility (OLCF)\footnote{This research was
supported by, and used the resources of, the Oak Ridge Leadership Computing
Facility, located in the National Center for Computational Sciences at ORNL,
which is managed by UT Battelle, LLC for the U.S. DOE (under the contract No.
DE-AC05-00OR22725).} at Oak Ridge National Laboratory (ORNL) has a long history
of deploying and running very-large-scale high-performance computing (HPC)
systems\footnote{\url{http://www.top500.org/site/48553}}. The facility hosted
the Jaguar supercomputer up until recently, which was upgraded to the Titan
supercomputer. In order to satisfy the I/O demand of such supercomputers (as
well as, other OLCF computational, analysis, and visualization clusters), OLCF
also hosts large-scale file and storage systems. Lustre has been OLCF's choice
as the distributed parallel file system.  The latest incarnation of such
large-scale file systems hosted at OLCF is Spider II\cite{spider2}. Spider II
is the upgrade of its predecessor, Spider, which was deployed in 2008.
Spider II, deployed in 2013, is designed to operate at over 1 TB/s peak
aggregate I/O throughput and has a 40 PB of raw disk capacity. As the scratch
file system connected to a leadership computing platform at the scale of Titan,
Spider II emphasizes \textit{capability} over \textit{capacity}. However, we
also recognize that there are a wide variety of scientific data and workloads
with different performance and data access requirements (e.g., RESTful
interface, S3-like API, cloud solution integration) which might not be
efficiently serviced by Lustre. OLCF is constantly evaluating new and emerging
file and storage system technologies.

@@

\begin{comment}
In comparison to other parallel file
systems, Ceph has a number of distinctive features:

\begin{itemize}

@@

As interesting and feature-rich as Ceph may be,  scalability and performance
are our top priorities due to the unique requirements our environment.  As part
of this study, we set up a dedicated testbed within OLCF to  evaluate Ceph.
Our goal was to investigate the feasibility of using the Ceph for future
large-scale scientific HPC storage deployments. This paper presents our
experience, results, and observations.  While evaluating our results, please
keep in mind that Ceph is still a relatively \textit{young} parallel file
system and its code base is changing rapidly. In between releases, we often
experienced different stability and performance outcomes.  We will try to make
clear in the writing when such changes occurred.

### 2013-08-30 testbed.tex
changes here and there

\section{Testbed Environment Description}
\label{sec:testbed}

We used Data Direct Networks' (DDN) SFA10K as the storage backend for this
evaluation. SFA10K organizes disks into various RAID levels by two
active-active RAID controllers. The exported RAID groups (LUNs) by these
controllers are driven by four server hosts (oss-[1-4]).  Each server host has two InfiniBand
(IB) QDR connections to the storage backend.  We used a single dual-port
Mellanox ConnectX IB QDR card per host.  By our calculation, this setup is
adequate to drive the SFA10K at its maximum theoretical throughput (roughly 12
GB/s). Server hosts and SFA10K connection diagram is illustrated in
Figure~\ref{fig:ddn-sfa10k}.

@@

All hosts  (client and servers) were configured with Redhat 6.3 and kernel
version 3.5.1 initially, and later upgraded to 3.9 (rhl-ceph image), Glibc
2.12 with syncfs support, locally patched.  We used the Ceph 0.48 and 0.55
release in the initial tests, upgraded to 0.64 and then to 0.67RC for a final
round of tests.

>>>>

\section{Testbed Environment and Test Methodology}
\label{sec:testbed}

We used Data Direct Networks' (DDN) SFA10K as the storage backend for this
evaluation. SFA10K organizes disks into various RAID levels by two
active-active RAID controllers. Exported RAID groups (LUNs) by these
controllers are driven by four server hosts (oss-[1-4]).  Each server host has
two InfiniBand (IB) QDR connections to the storage backend.  We used a single
dual-port Mellanox ConnectX IB QDR card per host.  By our calculation, this
setup is adequate to drive the SFA10K at its maximum theoretical throughput
(roughly 12 GB/s). Server hosts and SFA10K connection diagram is illustrated in
Figure~\ref{fig:ddn-sfa10k}.

@@

All hosts  (client and servers) were configured with Redhat 6.3 and kernel
version 3.5.1 initially, and later upgraded to 3.9, Glibc
2.12 with syncfs support, locally patched.  We used the Ceph 0.48 and 0.55
release in the initial tests, upgraded to 0.64 and then to 0.67RC for a final
round of tests.
